\LARGE Performance Evaluation of Xenomai 3

### 2015-10-21 paper.tex
eps is deprecated. always use pdflatex
use consistent xenomai 3
we need more insightful conclusion

%% insert eps pictures
%% use as \epsin{epsfile}{width_in_mm}{label}{caption}
\usepackage{epsfig}
\newcounter{figcounter}
\def\epsin #1#2#3#4{
\refstepcounter{figcounter} \label{#3}
\[
\mbox{
  \epsfxsize=#2mm
  \epsffile{#1.eps}
}
\]
%\vspace{0mm}
\begin{center}
  \parbox{7cm}{{\bf FIGURE \arabic{figcounter}:}\quad {\it #4 } } \\
\end{center}
}

@@

Xenomai 2 provides skins to emulate traditional RTOS, such as VxWorks and pSOS, and a number of projects have been migrated smoothly from one of the supported traditional RTOS to Xenomai. In order to use a similar approach to migrate traditional RTOS projects to native Linux as well, Xenomai 3.x was launched. Thus, the single kernel configuration, Mercury, in Xenomai 3 does rely on the real-time capabilities of the native Linux kernel. Often, applications will require the PREEMPT\_RT extension to be enabled in the target kernel, for delivering real-time services.

@@

The Linux kernel running under Xenomai 3 can be PREEMPT\_RT as well through the native option of Xenomai 3 for maximum API/ABI compatibility in real-time environments. For the tight latency requirements such as real-time networking, Xenomai 3 allows to switch to dual kernel configurations utilizing I-pipe for maximum real-time performance, which brings sligtly better performance than Xenomai 2. However, comparing to Xenomai 2, our results show the unexpected slowdown of timer-irq latency in stressed condition while Xenomai 3 was configured as the dual kernel configuration of Xenomai 3 though. From our performance evaluation, Xenomai 3 is known as the most flexible real-time option.

>>>>

@@

Xenomai 2 provides skins to emulate traditional RTOS, such as VxWorks and pSOS, and a number of projects have been migrated smoothly from one of the supported traditional RTOS to Xenomai. In order to use a similar approach to migrate traditional RTOS projects to native Linux as well, Xenomai 3 was launched. Thus, the single kernel configuration, Mercury, in Xenomai 3 does rely on the real-time capabilities of the native Linux kernel. Often, applications will require the PREEMPT\_RT extension to be enabled in the target kernel, for delivering real-time services.

@@

The Linux kernel running under Xenomai 3 can be PREEMPT\_RT as well through the native option of Xenomai 3 for maximum API/ABI compatibility in real-time environments. For the tight latency requirements such as real-time networking, Xenomai 3 allows to switch to dual kernel configurations utilizing I-pipe for maximum real-time performance, which brings sligtly better performance than Xenomai 2. However, comparing to Xenomai 2, our results show the unexpected slowdown of timer-irq latency in stressed condition while Xenomai 3 was configured as the dual kernel configuration of Xenomai 3 though.
